
### Tools needed for Cleaning, Organizing and Transforming Data in R
```{r}
library(tidyverse)
```


#### Cleaning Data Tools
- rename()
- rename_with()
- glimpse()
- select()
- clean_names()
- skim_without-charts()

#### Organising Data Tools

- filter()
- max()
- mean()
- summarize()
- arrange()
- group_by()
- drop_na()

#### Transforming Data Tools

- `%>%` 
- unite()
- separate()
- mutate()

#### Checking for Bias Tools

```{r}
library(SimDesign)
```

- bias(actual, predicted)


#### Summary statistics and visualization

Anscombe's quartet has four datasets that have nearly identical summary statistics.

```{r}
library(Tmisc)
```

```{r}
data(quartet)
```


```{r}
quartet %>% group_by(set) %>% summarize(mean(x), sd(x), mean(y), sd(y), cor(x,y))
```


The standard deviation can help us understand the spread of values in a dataset and show us how far each value is from the mean.


```{r}
ggplot(quartet, aes(x,y)) + geom_point() + geom_smooth(method=lm, se=FALSE) + facet_wrap(~set)
```



`search()` shows attached datasets and packages 

`detach()` remove attached datasets

```{r}
install.packages("datasauRus")
library(datasauRus)
```

```{r}
ggplot(datasaurus_dozen, aes(x=x, y=y, colour=dataset)) + geom_point() + 
                theme_void() + theme(legend.position = "none") + facet_wrap(~dataset, ncol = 3)
```

